\bf An Examination of Sport Climbing Competition Format and Scoring System

### 2021-07-29 manuscript/Rmd/draft.Rmd
Update Rmd + code

abstract: |
  The purpose of this paper is to investigate sport climbing, one of the sports making its debut on the Olympics stage at Tokyo 2020. In particular, we take a closer look at the controversial competition format and scoring system of sport climbing.

  ... Simulation. Data Analysis: drop and re-rank, correlations
# bibliography: bib_example.bib
output: rticles::asa_article
---

@@

In the Olympic sport climbing, there are 20 competitors at the start (in both men's and women's).  All 20 competitors compete in each of the three events in the qualification round, and their performances in each event are ranked from 1 to 20.  A competitors final score is then computed as the product of their ranks in the three events and the lower product is better.  Specifically, 
\begin{equation}
Score_i = R^S_i\times R^B_i\times R^L_i,
\end{equation} 
where $R^S_i$, $R^B_i$, and $R^L_i$ are the ranks of the $i$-th competitor in speed climbing, bouldering, and lead climbing, respectively.

The top 8 finishers in the qualification round advance to the finals where they once again compete in all three events, they are again ranked from 1 to 8, and their final score is the product of these three ranks in the final.  Whoever has the lowest product of ranks in the final wins the gold medal. This type of scoring system heavily rewards high finishes and relatively ignores poor finishes.  For instance, if climber A finished 1st, 20th, and 20th and climber B finished 10th, 10th, and 10th, climber B would have a score of 1000 whereas climber A would have a much better score of 400, despite finishing last in 2 out of 3 of the events.

@@

As a side note, rank product, genes

@@

We collected data on major climbing competitions from 2018 to 2020, including the 2020 Continental Championships of Europe, Africa, Oceania, Pan-America; 2019 and 2018 World Championships; 2018 Asian Games; and 2018 Youth Olympics. Data were obtained from various sources, including the event websites, Wikipedia, and the International Federation of Sport Climbing (IFSC). The main attributes of our datasets are the name and nationality of the climbers; bib number (for some competitions); the finishing place of climbers in speed climbing, bouldering, and lead climbing; the total score (which equals the product of event ranks); and the final rank. We utilize this data to compute the correlations between the event ranks and final table position, as well as to look at how often the final orderings change if one athlete is dropped and the ranks for each discipline are re-computed.

EDA

@@

# Results

## Simulations

qual <- bind_rows(qual_sim) %>% 
  mutate(qual_score = e1 * e2 * e3) %>% 
  group_by(sim) %>% 
  mutate(qual_rank = rank(qual_score, ties.method = "random")) %>%
  ungroup()
```

final <- final %>% 
  mutate(final_score = e1 * e2 * e3) %>% 
  group_by(sim) %>% 
  mutate(final_rank = rank(final_score, ties.method = "random")) %>%
  ungroup()
```

We conducted a simulation study to examine the rankings and scoring for climbers in both qualification and final rounds. For each round, we performed 10000 simulations, and this was accomplished by randomly assigning the ranks of each event to every participant, with the assumption that the ranks are uniformly distributed. After the completion of the simulations, we calculated the total scores for every simulated round, as well as the final standings for the climbing athletes. Table 
and
Figure
are numerical and visual summaries of final scores obtaining from our simulated data for the qualification round.

```{r}
mosaic::favstats(qual$qual_score)[-9] %>% 
  xtable(caption = "Descriptive statistics of simulated qualification scores") %>% 
  print()
```

```{r, fig.cap = "Histogram of qualification scores"}
qual %>%
  ggplot(aes(qual_score)) +
  geom_histogram(bins = 20, color = "white") + 
  labs(x = "Qualification Score",
       y = "Frequency")
  # theme(axis.title = element_text(size = 9),
  #       axis.text = element_text(size = 8))
```

The simulation results allow to answer questions about various topics, including the distributions of scores for qualifying and final rounds, and the probabilities of advancing to the finals or winning a medal, given certain conditions. For the qualification round, a climber is almost guaranteed to make the final round if they win the first event (with a 99.51% chance of advancing) or if they win at least one of the three climbing concentrations (99.48%). On the other hand, finishing last in the first event or in any event would certainly hurt an athlete's chance of finishing in the top 8, as the probabilities of a climber advancing given they finish last in the first and in any event are 0.1830 and 0.1885, respectively. In addition, the average score for qualification positions 1 to 8 are displayed in Table 1. We notice that on average, the minimum score that one should aim for in order to move on to the final round is 435 (for 8th rank).

```{r}
qual %>% 
  group_by(qual_rank) %>% 
  summarize(avg_adv_score = mean(qual_score)) %>% 
  filter(qual_rank <= 8) %>% 
  xtable(caption = "Average score for each qualifying rank") %>% 
  print()
```

```{r}
final %>% 
  group_by(final_rank) %>% 
  summarize(avg_score = mean(final_score)) %>% 
  xtable(caption = "Average score of medalists") %>% 
  print()
```

```{r, fig.cap = "Boxplots of scoring distribution for every qualification rank"}
qual %>% 
  mutate(qual_rank = factor(qual_rank)) %>% 
  ggplot(aes(x = qual_score, y = qual_rank)) +
  geom_boxplot()
```

## Data Analysis

@@

### Speed climbing vs lead and bouldering

@@

```{r, fig.cap = "Kendall's rank correlations - 2018 World Championship, Women's Qualification", fig.width = 6}
wq %>% 
  select(rank, speed, bould, lead) %>% 
  ggpairs(diag = "blank",
          axisLabels = "internal",
          upper = list(continuous = wrap("cor", method = "kendall", stars = FALSE))) +
  theme(panel.grid.major = element_blank())
```

### Drop and re-rank

>>>>

abstract: |
  The purpose of this paper is to investigate sport climbing, one of the sports making its debut on the Olympics stage at Tokyo 2020. In particular, we take a closer look at the controversial competition format and scoring system of sport climbing... Simulation. Data Analysis: drop and re-rank, correlations
# bibliography: bib_example.bib
output: rticles::asa_article
---

@@

At the 2020 Summer Olympics, both men's and women's sport climbing competitions begin with 20 climbers who has previously qualified for the Olympics from qualifying events held in 2019 and 2020. All 20 athletes compete in each of the three disciplines in the qualification round, and their performances in each concentration are ranked from 1 to 20.  A competitor's total score is then computed as the product of their ranks in the three events and the lower product is better; specifically, 
\begin{equation}
Score_i = R^S_i\times R^B_i\times R^L_i,
\end{equation} 
where $R^S_i$, $R^B_i$, and $R^L_i$ are the ranks of the $i$-th competitor in speed climbing, bouldering, and lead climbing, respectively.

The top 8 finishers in the qualification round advance to the finals where they once again compete in all three of speed climbing, bouldering, and lead climbing. The total score for each climber in the final stage is determined by multiplying their ranks in each discipline, similar to the qualification round. This implies that the climber with the lowest product of ranks in the final wins the gold medal. This type of scoring system heavily rewards high finishes and relatively ignores poor finishes.  For instance, if climber A finished 1st, 20th, and 20th and climber B finished 10th, 10th, and 10th, climber B would have a score of 1000 whereas climber A would have a much better score of 400, despite finishing last in 2 out of 3 of the events.

@@

The manuscript is outlined as follows. We first begin with some descriptions of the data and methods in Section 2. Our analyses and results are then presented in Sections 3 and 4. Finally, in Section 5, we summarize up of main findings and give a discussion to close out the paper.

@@

The first sets of data that we rely on are historical results from major climbing competitions in the past. We collected data on climbing contests that took place between 2018 and 2020, where the combined format was used to determine the scores and ranks of climbers. The events include the 2020 Continental Championships of Europe, Africa, Oceania, Pan-America; 2019 and 2018 World Championships; 2018 Asian Games; and 2018 Youth Olympics. Data were obtained from various sources, including the event websites, Wikipedia, and the International Federation of Sport Climbing (IFSC). The main attributes of our datasets are the name and nationality of the climbers; bib number (for some competitions); the finishing place of climbers in speed climbing, bouldering, and lead climbing; the total score (which equals the product of event ranks); and the final rank. We utilize this data to compute the correlations between the event ranks and final table position, as well as to look at how often the final orderings change if one athlete is dropped and the ranks for each discipline are re-computed.

Our second data source comes from a simulation study that we conducted, with the purpose of examining the rankings and scoring for climbers in both qualification and final rounds. For each round, we performed 10000 simulations, and this was accomplished by randomly assigning the ranks of each event to every participant, with the assumption that the ranks are uniformly distributed. After the completion of the simulations, we calculated the total scores for every simulated round, as well as the final standings for the climbing athletes. The simulation results allow to answer questions about various topics, including the distributions of scores for qualifying and final rounds, and the probabilities of advancing to the finals or winning a medal, given certain conditions.

Table 1 and Figure 1 are numerical and visual summaries of climbing total score obtained from our simulated data for the qualification round.

qual <- bind_rows(qual_sim) %>% 
  mutate(score = e1 * e2 * e3) %>% 
  group_by(sim) %>% 
  mutate(rank = rank(score, ties.method = "random")) %>%
  ungroup()
```

final <- final %>% 
  mutate(score = e1 * e2 * e3) %>% 
  group_by(sim) %>% 
  mutate(rank = rank(score, ties.method = "random")) %>%
  ungroup()

qual_final <- qual %>% 
  mutate(round = "Qualification") %>% 
  bind_rows(mutate(final, round = "Final")) %>% 
  mutate(round = fct_rev(round))
```

```{r}
mosaic::favstats(score ~ round, data = qual_final)[-10] %>% 
  xtable(caption = "Descriptive statistics of simulated scores for qualification and final rounds") %>% 
  print()
```

```{r, fig.cap = "Histogram of simulated scores for qualification and final rounds", fig.width = 6.4, fig.height = 3.2}
qual_final %>%
  ggplot(aes(score)) +
  geom_histogram(bins = 20, fill = "lightgray", color = "black") + 
  facet_wrap(~ round, scales = "free") +
  labs(x = "Score",
       y = "Frequency")
```

# Simulations

For the qualification round, a climber is almost guaranteed to make the final round if they win the first event (with a 99.51% chance of advancing) or if they win at least one of the three climbing concentrations (99.48%). On the other hand, finishing last in the first event or in any event would certainly hurt an athlete's chance of finishing in the top 8, as the probabilities of a climber advancing given they finish last in the first and in any event are 0.1830 and 0.1885, respectively. In addition, the average score for qualification positions 1 to 8 are displayed in Table 1. We notice that on average, the minimum score that one should aim for in order to move on to the final round is 435 (for 8th rank).

```{r}
qual %>% 
  group_by(rank) %>% 
  summarize(avg_adv_score = mean(score)) %>% 
  filter(rank <= 8) %>% 
  xtable(caption = "Average score for each qualifying rank") %>% 
  print()
```

```{r}
final %>% 
  group_by(rank) %>% 
  summarize(avg_score = mean(score)) %>% 
  xtable(caption = "Average score of medalists") %>% 
  print()
```

```{r, fig.cap = "Boxplots of scoring distribution for every qualification rank", eval = FALSE}
qual %>% 
  mutate(rank = factor(rank)) %>% 
  ggplot(aes(x = score, y = rank)) +
  geom_boxplot()
```

# Data Analysis

@@

@@

## Speed climbing vs lead and bouldering

@@

```{r, fig.cap = "Kendall's rank correlations - 2018 World Championship, Women's Qualification"}
wq %>% 
  select(rank, speed, bould, lead) %>% 
  ggpairs(diag = "blank",
          axisLabels = "internal",
          upper = list(continuous = wrap("cor", method = "kendall", stars = FALSE))) +
  theme(panel.grid.major = element_blank())
```

## Drop and re-rank

### 2021-07-29 manuscript/Rmd/draft.tex
Update Rmd + code

% !TeX program = pdfLaTeX
\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{graphicx,psfrag,epsf}
\usepackage{enumerate}
\usepackage{natbib}
\usepackage{textcomp}
\usepackage{float}
\usepackage[hyphens]{url} % not crucial - just used below for the URL
\usepackage{hyperref}
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

@@

\bigskip
\begin{abstract}
The purpose of this paper is to investigate sport climbing, one of the
sports making its debut on the Olympics stage at Tokyo 2020. In
particular, we take a closer look at the controversial competition
format and scoring system of sport climbing.

\ldots{} Simulation. Data Analysis: drop and re-rank, correlations
\end{abstract}

@@

In the Olympic sport climbing, there are 20 competitors at the start (in
both men's and women's). All 20 competitors compete in each of the three
events in the qualification round, and their performances in each event
are ranked from 1 to 20. A competitors final score is then computed as
the product of their ranks in the three events and the lower product is
better. Specifically, \begin{equation}
Score_i = R^S_i\times R^B_i\times R^L_i,
\end{equation} where \(R^S_i\), \(R^B_i\), and \(R^L_i\) are the ranks
of the \(i\)-th competitor in speed climbing, bouldering, and lead
climbing, respectively.

The top 8 finishers in the qualification round advance to the finals
where they once again compete in all three events, they are again ranked
from 1 to 8, and their final score is the product of these three ranks
in the final. Whoever has the lowest product of ranks in the final wins
the gold medal. This type of scoring system heavily rewards high
finishes and relatively ignores poor finishes. For instance, if climber
A finished 1st, 20th, and 20th and climber B finished 10th, 10th, and
10th, climber B would have a score of 1000 whereas climber A would have
a much better score of 400, despite finishing last in 2 out of 3 of the
events.

@@

We collected data on major climbing competitions from 2018 to 2020,
including the 2020 Continental Championships of Europe, Africa, Oceania,
Pan-America; 2019 and 2018 World Championships; 2018 Asian Games; and
2018 Youth Olympics. Data were obtained from various sources, including
the event websites, Wikipedia, and the International Federation of Sport
Climbing (IFSC). The main attributes of our datasets are the name and
nationality of the climbers; bib number (for some competitions); the
finishing place of climbers in speed climbing, bouldering, and lead
climbing; the total score (which equals the product of event ranks); and
the final rank. We utilize this data to compute the correlations between
the event ranks and final table position, as well as to look at how
often the final orderings change if one athlete is dropped and the ranks
for each discipline are re-computed.

EDA

@@

\hypertarget{results}{%
\section{Results}\label{results}}

\hypertarget{simulations}{%
\subsection{Simulations}\label{simulations}}

We conducted a simulation study to examine the rankings and scoring for
climbers in both qualification and final rounds. For each round, we
performed 10000 simulations, and this was accomplished by randomly
assigning the ranks of each event to every participant, with the
assumption that the ranks are uniformly distributed. After the
completion of the simulations, we calculated the total scores for every
simulated round, as well as the final standings for the climbing
athletes. Table and Figure are numerical and visual summaries of final
scores obtaining from our simulated data for the qualification round.

\begin{table}[ht]
\centering
\caption{Descriptive statistics of simulated qualification scores} 
\begin{tabular}{rrrrrrrr}
  \hline
min & Q1 & median & Q3 & max & mean & sd & n \\ 
  \hline
1.00 & 240.00 & 684.00 & 1638.00 & 8000.00 & 1158.84 & 1273.48 & 200000 \\ 
   \hline
\end{tabular}
\end{table}

\begin{figure}[H]
\centering
\includegraphics{draft_files/figure-latex/unnamed-chunk-5-1.pdf}
\caption{Histogram of qualification scores}
\end{figure}

The simulation results allow to answer questions about various topics,
including the distributions of scores for qualifying and final rounds,
and the probabilities of advancing to the finals or winning a medal,
given certain conditions. For the qualification round, a climber is
almost guaranteed to make the final round if they win the first event
(with a 99.51\% chance of advancing) or if they win at least one of the
three climbing concentrations (99.48\%). On the other hand, finishing
last in the first event or in any event would certainly hurt an
athlete's chance of finishing in the top 8, as the probabilities of a
climber advancing given they finish last in the first and in any event
are 0.1830 and 0.1885, respectively. In addition, the average score for
qualification positions 1 to 8 are displayed in Table 1. We notice that
on average, the minimum score that one should aim for in order to move
on to the final round is 435 (for 8th rank).

\begin{table}[ht]
\centering
\caption{Average score for each qualifying rank} 
\begin{tabular}{rr}
  \hline
qual\_rank & avg\_adv\_score \\ 
  \hline
  1 & 36.02 \\ 
    2 & 73.61 \\ 
    3 & 115.40 \\ 
    4 & 162.23 \\ 
    5 & 216.00 \\ 
    6 & 278.16 \\ 
    7 & 350.33 \\ 
    8 & 434.59 \\ 
   \hline
\end{tabular}
\end{table}

\begin{table}[ht]
\centering
\caption{Average score of medalists} 
\begin{tabular}{rr}
  \hline
final\_rank & avg\_score \\ 
  \hline
  1 & 9.67 \\ 
    2 & 20.41 \\ 
    3 & 33.26 \\ 
    4 & 50.59 \\ 
    5 & 74.76 \\ 
    6 & 110.05 \\ 
    7 & 164.43 \\ 
    8 & 265.78 \\ 
   \hline
\end{tabular}
\end{table}

\begin{figure}[H]
\centering
\includegraphics{draft_files/figure-latex/unnamed-chunk-8-1.pdf}
\caption{Boxplots of scoring distribution for every qualification rank}
\end{figure}

\hypertarget{data-analysis}{%
\subsection{Data Analysis}\label{data-analysis}}

\hypertarget{speed-climbing-vs-lead-and-bouldering}{%
\subsubsection{Speed climbing vs lead and
bouldering}\label{speed-climbing-vs-lead-and-bouldering}}

@@

\begin{figure}[H]
\centering
\includegraphics{draft_files/figure-latex/unnamed-chunk-10-1.pdf}
\caption{Kendall's rank correlations - 2018 World Championship, Women's
Qualification}
\end{figure}

\hypertarget{drop-and-re-rank}{%
\subsubsection{Drop and re-rank}\label{drop-and-re-rank}}

@@

\begin{figure}[H]
\centering
\includegraphics{draft_files/figure-latex/unnamed-chunk-12-1.pdf}
\caption{This figure shows the rankings of the Men's Sport Climbing
Final at the 2018 Youth Olympics. Each panel represents the dropped
rank, with 0 being the original final standings. The cases where a
change in ordering happened are highlighted.}
\end{figure}

\begin{figure}[H]
\centering
\includegraphics{draft_files/figure-latex/unnamed-chunk-13-1.pdf}
\caption{This figure shows the final rankings of 2018 Youth Olympics
Women's Final. Each panel represents the dropped rank, with 0 being the
original final standings. The cases where a change in ordering happened
are highlighted.}
\end{figure}

>>>>

% !TeX program = pdfLaTeX
\documentclass[12pt]{article}
\usepackage{amsmath}
\usepackage{graphicx,psfrag,epsf}
\usepackage{enumerate}
\usepackage{natbib}
\usepackage{textcomp}
\usepackage[hyphens]{url} % not crucial - just used below for the URL
\usepackage{hyperref}
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

@@

\bigskip
\begin{abstract}
The purpose of this paper is to investigate sport climbing, one of the
sports making its debut on the Olympics stage at Tokyo 2020. In
particular, we take a closer look at the controversial competition
format and scoring system of sport climbing\ldots{} Simulation. Data
Analysis: drop and re-rank, correlations
\end{abstract}

@@

At the 2020 Summer Olympics, both men's and women's sport climbing
competitions begin with 20 climbers who has previously qualified for the
Olympics from qualifying events held in 2019 and 2020. All 20 athletes
compete in each of the three disciplines in the qualification round, and
their performances in each concentration are ranked from 1 to 20. A
competitor's total score is then computed as the product of their ranks
in the three events and the lower product is better; specifically,
\begin{equation}
Score_i = R^S_i\times R^B_i\times R^L_i,
\end{equation} where \(R^S_i\), \(R^B_i\), and \(R^L_i\) are the ranks
of the \(i\)-th competitor in speed climbing, bouldering, and lead
climbing, respectively.

The top 8 finishers in the qualification round advance to the finals
where they once again compete in all three of speed climbing,
bouldering, and lead climbing. The total score for each climber in the
final stage is determined by multiplying their ranks in each discipline,
similar to the qualification round. This implies that the climber with
the lowest product of ranks in the final wins the gold medal. This type
of scoring system heavily rewards high finishes and relatively ignores
poor finishes. For instance, if climber A finished 1st, 20th, and 20th
and climber B finished 10th, 10th, and 10th, climber B would have a
score of 1000 whereas climber A would have a much better score of 400,
despite finishing last in 2 out of 3 of the events.

@@

The first sets of data that we rely on are historical results from major
climbing competitions in the past. We collected data on climbing
contests that took place between 2018 and 2020, where the combined
format was used to determine the scores and ranks of climbers. The
events include the 2020 Continental Championships of Europe, Africa,
Oceania, Pan-America; 2019 and 2018 World Championships; 2018 Asian
Games; and 2018 Youth Olympics. Data were obtained from various sources,
including the event websites, Wikipedia, and the International
Federation of Sport Climbing (IFSC). The main attributes of our datasets
are the name and nationality of the climbers; bib number (for some
competitions); the finishing place of climbers in speed climbing,
bouldering, and lead climbing; the total score (which equals the product
of event ranks); and the final rank. We utilize this data to compute the
correlations between the event ranks and final table position, as well
as to look at how often the final orderings change if one athlete is
dropped and the ranks for each discipline are re-computed.

Our second data source comes from a simulation study that we conducted,
with the purpose of examining the rankings and scoring for climbers in
both qualification and final rounds. For each round, we performed 10000
simulations, and this was accomplished by randomly assigning the ranks
of each event to every participant, with the assumption that the ranks
are uniformly distributed. After the completion of the simulations, we
calculated the total scores for every simulated round, as well as the
final standings for the climbing athletes. The simulation results allow
to answer questions about various topics, including the distributions of
scores for qualifying and final rounds, and the probabilities of
advancing to the finals or winning a medal, given certain conditions.

Table 1 and Figure 1 are numerical and visual summaries of climbing
total score obtained from our simulated data for the qualification
round.

\begin{table}[ht]
\centering
\caption{Descriptive statistics of simulated scores for qualification and final rounds} 
\begin{tabular}{lrrrrrrrr}
  \hline
round & min & Q1 & median & Q3 & max & mean & sd & n \\ 
  \hline
Qualification & 1.00 & 240.00 & 684.00 & 1638.00 & 8000.00 & 1158.84 & 1273.48 & 200000 \\ 
  Final & 1.00 & 24.00 & 60.00 & 126.00 & 512.00 & 91.12 & 91.35 & 80000 \\ 
   \hline
\end{tabular}
\end{table}

\begin{figure}
\centering
\includegraphics{draft_files/figure-latex/unnamed-chunk-5-1.pdf}
\caption{Histogram of simulated scores for qualification and final
rounds}
\end{figure}

\hypertarget{simulations}{%
\section{Simulations}\label{simulations}}

For the qualification round, a climber is almost guaranteed to make the
final round if they win the first event (with a 99.51\% chance of
advancing) or if they win at least one of the three climbing
concentrations (99.48\%). On the other hand, finishing last in the first
event or in any event would certainly hurt an athlete's chance of
finishing in the top 8, as the probabilities of a climber advancing
given they finish last in the first and in any event are 0.1830 and
0.1885, respectively. In addition, the average score for qualification
positions 1 to 8 are displayed in Table 1. We notice that on average,
the minimum score that one should aim for in order to move on to the
final round is 435 (for 8th rank).

\begin{table}[ht]
\centering
\caption{Average score for each qualifying rank} 
\begin{tabular}{rr}
  \hline
rank & avg\_adv\_score \\ 
  \hline
  1 & 36.02 \\ 
    2 & 73.61 \\ 
    3 & 115.40 \\ 
    4 & 162.23 \\ 
    5 & 216.00 \\ 
    6 & 278.16 \\ 
    7 & 350.33 \\ 
    8 & 434.59 \\ 
   \hline
\end{tabular}
\end{table}

\begin{table}[ht]
\centering
\caption{Average score of medalists} 
\begin{tabular}{rr}
  \hline
rank & avg\_score \\ 
  \hline
  1 & 9.67 \\ 
    2 & 20.41 \\ 
    3 & 33.26 \\ 
    4 & 50.59 \\ 
    5 & 74.76 \\ 
    6 & 110.05 \\ 
    7 & 164.43 \\ 
    8 & 265.78 \\ 
   \hline
\end{tabular}
\end{table}

\hypertarget{data-analysis}{%
\section{Data Analysis}\label{data-analysis}}

@@

\hypertarget{speed-climbing-vs-lead-and-bouldering}{%
\subsection{Speed climbing vs lead and
bouldering}\label{speed-climbing-vs-lead-and-bouldering}}

@@

\begin{figure}
\centering
\includegraphics{draft_files/figure-latex/unnamed-chunk-10-1.pdf}
\caption{Kendall's rank correlations - 2018 World Championship, Women's
Qualification}
\end{figure}

\hypertarget{drop-and-re-rank}{%
\subsection{Drop and re-rank}\label{drop-and-re-rank}}

@@

\begin{figure}
\centering
\includegraphics{draft_files/figure-latex/unnamed-chunk-12-1.pdf}
\caption{This figure shows the rankings of the Men's Sport Climbing
Final at the 2018 Youth Olympics. Each panel represents the dropped
rank, with 0 being the original final standings. The cases where a
change in ordering happened are highlighted.}
\end{figure}

\begin{figure}
\centering
\includegraphics{draft_files/figure-latex/unnamed-chunk-13-1.pdf}
\caption{This figure shows the final rankings of 2018 Youth Olympics
Women's Final. Each panel represents the dropped rank, with 0 being the
original final standings. The cases where a change in ordering happened
are highlighted.}
\end{figure}
